\documentclass{article}
\usepackage[left = 3cm, right = 3cm]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

\makeatletter
\renewcommand*{\UrlTildeSpecial}{%
  \do\~{%
    \mbox{%
      \fontfamily{ptm}\selectfont
      \textasciitilde
    }%
  }%  
}%    
\let\Url@force@Tilde\UrlTildeSpecial
\makeatother

\begin{document}
\begin{Huge}
\noindent Lihua Lei
\end{Huge}

\vspace{5mm}
\begin{minipage}{0.6\linewidth}
  \flushleft
\noindent Sequoia Hall, 390 Serra Mall, Stanford University \\
\noindent Stanford, CA 94305-4020
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
  Website: \url{https://lihualei71.github.io}\\
  Email: \,\,\,\,\,lihualei@stanford.edu
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Education}
\end{large}
\vspace{5mm}

\begin{minipage}{0.65\linewidth}
\noindent Postdoctoral Researcher, Stanford University.\\
Advisor: Emmanuel Cand\`{e}s\\

\noindent Ph.D. Statistics, University of California, Berkeley.\\
Advisors: Peter, J. Bickel, and Michael, I. Jordan.\\

\noindent B.S. Statistics, Peking University. \\
Undergraduate Thesis Advisor: Song Xi, Chen.
\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
\vspace{-5mm}
9/2019 - present\\
~\\
~\\
8/2014 - 8/2019 \\
~\\
~\\
9/2010 - 6/2014\\
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Awards}
\end{large}

\vspace{5mm}

Eric Lehmann Citation (Annual Dissertation Award in Theoretical Statistics), 2019.

\vspace{2mm}

Citadel Fellowship, 2017-2018.

\vspace{2mm}

Outstanding Graduate Student Instructor Award, 2016.

\vspace{2mm}
ICML (International Conference on Machine Learning) Travel Award, 2016.

\vspace{2mm}
ACIC (Atlantic Causal Inference Conference) Travel Award, 2018.

\vspace{2mm}
Scholarship from The Sally and Terry Speed Graduate Support Fund, 2015.

\vspace{5mm}
\begin{large}
\noindent \textbf{Teaching Experiences}
\end{large}
\vspace{5mm}

TA, Statistics 210A, Theoretical Statistics A, Fall 2015 (taught by Michael, I. Jordan). 

% \vspace{2mm}
% Lecturer, Complementary Session for Statistics 210A, Fall 2015.

% \hspace{4mm} Self-prepared weekly lectures, covering Bayesian inference and hypothesis testing.

\vspace{2mm}
TA, Statistics 210B, Theoretical Statistics B, Spring 2016 (taught by Martin, J. Wainright). 

% \vspace{2mm}
% Lecturer, Complementary Session for Statistics 210B, Spring 2016.

% \hspace{4mm} Self-prepared weekly lectures, covering learning theories, concentration inequalities, 

% \hspace{4mm} high dimensional geometry, sparse linear regression, compressed sensing and kernel theories.

\vspace{5mm}
\begin{large}
\noindent \textbf{Research Experiences}
\end{large}
\vspace{5mm}

\begin{large}
\noindent Research Interests
\end{large}

\vspace{3mm}
Conformal Inference; Causal Inference; Multiple hypothesis testing;

Network analysis; High dimensional statistical inference; 

Stochastic optimization; Econometrics

\vspace{3mm}

\clearpage
\begin{large}
\noindent Journal Publications \footnote{$\ast$ = alphabetical ordering or equal contribution}
\end{large}

\begin{enumerate}
\item Fithian, W. and \textbf{Lei, L.} (2021) Conditional calibration for false discovery rate control under dependence. To appear in \emph{Annals of Statistics (AoS)}.
\item Bates, S.*, Angelopoulos, A.*, \textbf{Lei, L.}*, Malik, J., and Jordan, M. I. (2021) Distribution-Free, Risk-Controlling Prediction Sets. \emph{Journal of the ACM (JACM)}, 68(6), 1–34.
\item Loper, J. H.*, \textbf{Lei, L.}*, Fithian, W., and Tansey, W. (2021) Smoothed Nested Testing on Directed Acyclic Graphs. To appear in \emph{Biometrika}.
\item \textbf{Lei, L.} and Cand\`{e}s, E. J. (2021) Conformal Inference of Counterfactuals and Individual Treatment Effects. To appear in \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}.
\item \textbf{Lei, L.} and Ding, P. (2020) Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. To appear in \emph{Biometrika}.
\item Li, T., \textbf{Lei, L.}, Bhattacharyya, S., Sarkar, P., Bickel, P. J., and Levina, E. (2020) Hierarchical community detection by recursive partitioning. To appear in \emph{Journal of the American Statistical Association (JASA)}.
\item \textbf{Lei, L.} and Bickel, P. J. (2020) An Assumption-Free Exact Test For Fixed-Design Linear Models With Exchangeable Errors. \emph{Biometrika}, 108(2), 397-412.
\item \textbf{Lei, L.}, Ramdas, A., and Fithian, W. (2020) A general interactive framework for FDR control under structural constraints. \emph{Biometrika}, 108(2), 253-267.
\item \textbf{Lei, L.} and Jordan, M. I. (2020) On the Adaptivity of Stochastic Gradient-Based Optimization. \emph{SIAM Journal on Optimization (SIOPT)}, 30(2), 1473-1500.
\item D'Amour, A., Ding, P., Feller, A., \textbf{Lei, L.}, and Sekhon, J. (2019) Overlap in High Dimensional Observational Studies. \emph{Journal of Econometrics (JoE)}, 221(2), 644-654.
\item \textbf{Lei, L.}, and Fithian, W. (2018). AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}, 80(4), 649-679.
\item \textbf{Lei, L.}, Bickel, P. J., and El Karoui, N. (2018). Asymptotics For High Dimensional Regression M-Estimates: Fixed Design Results. \emph{Probability Theory and Related Fields (PTRF)}, 172(3-4), 983-1079.
\item Chen, S. X., \textbf{Lei, L.}, and Tu, Y. (2016). Functional Coefficient Moving Average Model with Applications to forecasting Chinese CPI. \emph{Statistica Sinica}, 26, 1649-1672.
\end{enumerate}

\begin{large}
\noindent Conference Publications
\end{large}

\begin{enumerate}
\item Elibol, M., \textbf{Lei, L.}, and Jordan, M. I. (2020). Variance Reduction with Sparse Gradients. To appear in \emph{International Conference on Learning Representations (ICLR)}
\item Ye, Y., \textbf{Lei, L.}, and Ju, C. (2018). HONES: A Fast and Tuning-free Homotopy Method For Online Newton Step. In \emph{Proceedings of the 20th International Conference on Artificial Intelligence and Statistics (AISTATS)}.
\item \textbf{Lei, L.}, Ju, C., Chen, J., and Jordan, M. I. (2017). Nonconvex Finite-Sum Optimization Via SCSG Methods. In \emph{Proceedings of the 30th Advances in Neural Information Processing Systems (Neurips)}.
\item \textbf{Lei, L.} and Jordan, M. I. (2017). Less than a Single Pass: Stochastically Controlled Stochastic Gradient. In \emph{Proceedings of the 20th International Conference on Artificial Intelligence and Statistics (AISTATS)}.
\item \textbf{Lei, L.} and Fithian, W. (2016). Power of Ordered Hypothesis Testing. In \emph{Proceedings of the 33th International Conference on Machine Learning (ICML)}.
\end{enumerate}

\begin{large}
\noindent Under Revision
\end{large}

\begin{enumerate}
\item Bates, S.*, Cand\`{e}s, E. J.*, \textbf{Lei, L.}*, Romano, Y.*, and Sesia, M.* (2021) Testing for Outliers with Conformal p-values. \emph{ArXiv e-prints, abs/2104.08279}. Under major revision at \emph{Annals of Statistics (AoS)}.
\item Cand\`{e}s, E. J.*, \textbf{Lei, L.}*, Ren, Z.* (2021) Conformalized Survival Analysis. \emph{ArXiv e-prints, abs/2103.09763}. Under major revision at \emph{Journal of the Royal Statistical Society: Series B (JRSS-B)}.
\item Horv\'{a}th, S.*, \textbf{Lei, L.}*, Richt\'{a}rik, P., and Jordan, M. I. (2020) Adaptivity of Stochastic Gradient Methods for Nonconvex Optimization. \emph{ArXiv e-prints, abs/2002.05359}. Under minor revision at \emph{SIAM Journal on Mathematics of Data Science (SIMODS)}.
\end{enumerate}

\begin{large}
\noindent Preprints and Submissions
\end{large}

\begin{enumerate}
\item Angelopoulos, A.*, Bates, S.*, Cand\`{e}s, E. J.*, Jordan, M. I.*, and \textbf{Lei, L.}* (2021) Learn then Test: Calibrating Predictive Algorithms to Achieve Risk Control. \emph{Arxiv e-prints, abs/2110.01052}.
\item Arkhangelsky, D.*, Imbens, G. W.*, \textbf{Lei, L.}*, and Luo, X.* (2021) Double-Robust Two-Way-Fixed-Effects Regression For Panel Data. \emph{Arxiv e-prints, abs/2107.13737}.
\item Yang, C., \textbf{Lei, L.}, Ho, N., and Fithian, W. (2021) BONuS: Multiple multivariate testing with a data-adaptive test statistic. \emph{ArXiv e-prints, abs/2106.15743}.
\item \textbf{Lei, L.}*, Li, X.*, and Lou, X.* (2020) Consistency of Spectral Clustering on Hierarchical Stochastic Block Models. \emph{ArXiv e-prints, abs/2004.14531}.
\item \textbf{Lei, L.} (2019) Unified $\ell_{2\rightarrow\infty}$ Eigenspace Perturbation Theory for Symmetric Random Matrices. \emph{ArXiv e-prints, abs/1909.04798}.
\end{enumerate}

\begin{large}
\noindent Software
\end{large}

\begin{enumerate}
\item \texttt{adaptMT}: \texttt{R} package on Adaptive P-value Thresholding (on CRAN);
\item \texttt{cfcausal}: \texttt{R} package on conformal inference of counterfactuals and individual treatment effects (on github);
\item \texttt{dbh}: \texttt{R} package on dependence-adjusted Benjamini-Hochberg and general step-up procedures (on github);
\item \texttt{mkn}: \texttt{R} package on multiple knockoffs based inference (on github).
\item \texttt{ovalue}: \texttt{R} package on distribution-free assessment of population overlap (O-values) for observational studies (on github).
\end{enumerate}

\vspace{5mm}
\begin{large}
\noindent \textbf{Professional Services}
\end{large}
\vspace{5mm}

\begin{large}
\noindent Invited Talks (no interview/job talks)
\end{large}

\begin{enumerate}
\item Double-Robust Two-Way-Fixed-Effects Regression For Panel Data. \emph{One World YoungStatS (Webinar)}, Dec. 2021.
\item AdaPT: An interactive procedure for multiple testing with side information. \emph{At Journal of Royal Statistical Society Webinar}, Dec. 2021.  
\item Conformal Inference of Counterfactuals and Time-to-event Outcomes. \emph{At University of Washington (Statistics Seminar)}, Oct. 2021.
\item Double-Robust Two-Way-Fixed-Effects Regression For Panel Data. \emph{University of California, Davis (Econometrics Seminar)}, Oct. 2021.
\item Double-Robust Two-Way-Fixed-Effects Regression For Panel Data. \emph{Harvard University (Econometrics Workshop)}, Sep. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{Temple University (Statistics Seminar)}, Sep. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{New York University (Data Science Lunch Seminar)}, Sep. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{ICSA Applied Statistics Symposium}, Sep. 2021.
\item Testing for Outliers with Conformal p-values. \emph{At 12th International Conference on Multiple Comparison Procedures (MCP)}, Aug. 2021.
\item Distribution-Free Assessment of Population Overlap in Observational Studies. \emph{At ICML "Neglected Assumptions of Causal Infernece" workshop}, Aug. 2021.
\item Conformalized Survival Analysis. \emph{At IFDS Summer Workshop}, Aug. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At INFORMS Virtual Healthcare Conference}, Jul. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At The Hong Kong University of Science \& Technology}, Jun. 2021.
\item AdaPT: An interactive procedure for multiple testing with side information. \emph{At WNAR}, Jun. 2021.
\item Conformal Inference of Counterfactuals and Time-to-event Outcomes. \emph{At ETH Z\"{u}rich (Young Data Science Seminar)}, Jun. 2021.
\item Hierarchical Community Detection for Heterogeneous and Multi-scaled Networks. \emph{At University of California, Berkeley (Neyman Seminar)}, May. 2021.
\item Conformal Inference of Counterfactuals and Time-to-event Outcomes. \emph{At Stanford University (Statistics Seminar)}, May. 2021.
\item Conformal Inference of Counterfactuals and Time-to-event Outcomes. \emph{At University of Chicago (Statistics Seminar)}, May. 2021.
\item Hierarchical Community Detection for Heterogeneous and Multi-scaled Networks. \emph{At Stanford University (RAIN Seminar)}, Apr. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At U Chicago Crime Lab (Data Science Meeting)}, Apr. 2021.
\item Cyclic Permutation Test for Linear Models. \emph{At University of Chicago, Booth School of Business (Econometrics and Statistics Colloquium Workshop)}, Apr. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At University of Maryland, Baltimore County (Statistics Seminar)}, Apr. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Dataiku research webinar}, Apr. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Northwestern University (Biostatistics \& Statistics Joint Seminar Series)}, Apr. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At University of Manchester (CfE Biostatistics Forum)}, Mar. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At The London School of Hygiene \& Tropical Medicine (LSHTM)}, Mar. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Computer Vision Talks Webinar}, Mar. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Facebook Core Data Science}, Mar. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Univerity of California, Los Angeles (Big Data and ML Seminar)}, Feb. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Univerity of Missouri (Biostatistics Group Seminar)}, Feb. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Leiden Univerity (Stéphanie van der Pas and Aad van der Vaart's group meeting)}, Feb. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Twitter}, Feb. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Stitch Fix}, Feb. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Rutgers University (Statistics Department Seminar)}, Feb. 2021.
\item Distribution-Free Assessment of Population Overlap in Observational Studies. \emph{At University of Pennsylvania (Statistics Department Seminar)}, Jan. 2021.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Lyft}, Dec. 2020.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At John Hopkins University (Causal Reading Group)}, Dec. 2020.
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At Florida State University (Hongyuan Cao's Class, Guest Lecture)}, Nov. 2020. 
\item Adaptivity of Stochastic Gradient-based Methods. \emph{At University of California, Berkeley (Jiantao Jiao's group}, Oct. 2020. 
\item Hierarchical Community Detection for Heterogeneous and Multi-scaled Networks. \emph{At University of North Carolina at Chapel Hill (Statistics Department Seminar)}, Oct. 2020. 
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Peking University (Biostatistics Department Seminar)}, Oct. 2020.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At The 2020 Pacific Causal Inference Conference}, Sep. 2020.
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At Online Causal Inference Seminar}, Jul. 2020.
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At International Seminar on Selective Inference}, Jul. 2020. 
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At Southwestern University of Finance and Economics}, Jul. 2020. 
\item Conformal Inference of Counterfactuals and Individual Treatment Effects. \emph{At 2020 BAAI Conference}, Jun. 2020. 
\item Fair and Efficient Allocation of Medical Resources During COVID-19. \emph{At Journal Club, Stanford University}, Jun. 2020.
\item Survival Analysis of COVID-19 Patients. \emph{At Data Studio, Stanford University}, May. 2020.
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At University of California, Berkeley (Michael I. Jordan's group)}, May. 2020. 
\item Fair and Efficient Allocation of Medical Resources During COVID-19. \emph{At University of California, Berkeley (Sandrine Dudoit's group)}, May. 2020. 
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At WNAR 2020 Annual Meeting}, Jun. 2020. (Cancelled due to COVID-19).
\item Unified $\ell_{2\rightarrow\infty}$ Eigenspace Perturbation Theory for Symmetric Random Matrices. \emph{At SIAM Conference on Mathematics of Data Science (MDS20)}, May. 2020. (Cancelled due to COVID-19).
\item BONuS: Adaptive Multiple Testing With Multivariate Test Statistics. \emph{At Banff Workshop}, Mar. 2020. (Cancelled due to COVID-19).
\item Model-Free Assessment of Overlap in Observational Studies. \emph{At University of California, Berkeley (Causal Reading Group)}, Jan. 2020.
\item Model-Free Assessment of Overlap in Observational Studies. \emph{SAMSI Workshop At Duke University)}, Dec. 2019.
\item BONuS: Adaptive Multiple Testing With Multivariate Test Statistics. \emph{At Facebook Core Data Science}, Nov. 2019.
\item Doubly robust two-way fixed effects regression for panel data. \emph{Third Annual Berkeley-Stanford Econometrics Jamboree)}, Oct. 2019.
\item Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{Joint Statistical Meeting, Topic Contributed Session}, Aug. 2019.
\item Hierarchical community detection by recursive partitioning. \emph{ICSA Applied Statistics Symposium}, Jun. 2019.
\item Model-Free Assessment of Overlap in Observational Studies. \emph{At Yale University (Quantitative Research Methods Workshop)}, Feb. 2019.
\item Hierarchical community detection by recursive partitioning. \emph{At University of California, Davis (Statistics Student Seminar)}, Jan. 2019.
\item Model-Free Assessment of Overlap in Observational Studies. \emph{At Stanford University (Stefan Wager's group)}, Jan. 2019.
\item Statistical Inference in Moderate Dimensions. \emph{At University of South California (Statistics Department Seminar)}, Dec. 2018.
\item Hierarchical community detection by recursive bi-partitioning. \emph{At University of Michigan (Liza Levina's group)}, Oct. 2018.
\item Statistical Inference in Moderate Dimensions. \emph{At University of Michigan (Student Seminar)}, Oct. 2018.
\item Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{At University of Michigan (Xuming He's group)}, Oct. 2018.
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{International Conference on Econometrics and Statistics (EcoSta)}, Jun. 2018.
\item Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{Atlantic Causal Inference Conference (ACIC)}, May. 2018.
\item Stochastically Controlled Stochastic Gradient (SCSG) Method. \emph{At University of California, Davis (Cho-Jui Hsieh's group)}, Mar. 2018.
\item AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At Stanford University (David Tse's group)}, Feb. 2018.
\item Asymptotics For High Dimensional Regression M-Estimates: Fixed Design Results. \emph{Berkeley-Stanford Econometrics Jamboree}, Nov. 2017. 
\end{enumerate}
 
\vspace{5mm}

% \begin{large}
% \noindent Contributed Talks and Poster Presentation
% \end{large}

% \vspace{2mm}
% Workshop on Higher-Order Asymptotics and Post-Selection Inference (WHOA-PSI), 2018.

% \vspace{2mm}
% European Causal Inference Meeting (EuroCIM), 2018.

% \vspace{2mm}
% Neural Information Processing Systems (NIPS), 2017.

% \vspace{2mm}
% International Conference on Multiple Comparison Procedures (MCP), 2017.

% \vspace{2mm}
% International Conference on Artificial Intelligence and Statistics (AISTATS), 2017.

% \vspace{2mm}
% Joint Statistical Meetings (JSM), 2016, 2018.

% \vspace{2mm}
% International Conference on Machine Learning (ICML), 2016.

% \vspace{2mm}
% Stanford-Berkeley Joint Colloquium, 2015, 2016, 2017.

% \vspace{2mm}
% Berkeley Statistics Annual Research Symposium (BSTARS), 2017, 2018.

% \newpage 
\vspace{5mm}
\begin{large}
\noindent Reviewing (revision review excluded)
\end{large}

\vspace{2mm}
\noindent \textbf{Statistics Journals (36): }(\#papers in parentheses) Annals of Statistics (AoS, 5), Journal of the American Statistical Association (JASA, 5), Biometrika (4), Journal of the Royal Statistical Society-Series A (JRSS-A, 1), Journal of the Royal Statistical Society-Series B (JRSS-B, 3), Bernoulli (1), Electronic Journal of Statistics (EJS, 2), Biometrics (3), Journal of Causal Inference (JCL, 2), Stat (1), Springer Book (1), SpringerBriefs (1), International Journal of Biostatistics (IJB, 1), Journal of Computational and Graphical Statistics (JCGS, 1), Statistica Sinica (1), International Journal of Approximate Reasoning (IJA, 1), Statistics in Biosciences (SIBS, 1), Journal of Statistical Planning and Inference (JSPI, 1)

\vspace{2mm}
\noindent \textbf{Other Journals (18): }(\#papers in parentheses) SIAM Journal on Mathematics of Data Science (SIMODS, 1), Operations Research (1), Management Science (1), Journal of Machine Learning Research (JMLR, 6), Transactions on Pattern Analysis and Machine Intelligence (TPAMI, 3), Computational Optimization and Applications (COAP, 1), Optimization Methods and Software (GOMS, 1), Artificial Intelligence (1), Information and Inference: A Journal of the IMA (IMAIAI, 1), Journal of Applied Econometrics (JAE, 1), Vietnam Journal of Mathematics (VJOM, 1)

\vspace{2mm}
\noindent \textbf{Conferences: }(year in parentheses) ICML (2019, 2020, 2021), NeurlPS (2019, 2020, 2021), COLT (2019, 2020, 2021), AISTATS (2019), UAI (2020, 2021)

\vspace{5mm}
\begin{large}
\noindent Other Academic Services
\end{large}

\begin{itemize}
\item Co-organizer of the International Seminar on Selective Inference (with Will Fithian, Rina Barber and Daniel Yekutieli).
\item Co-organizer of the GRoup-Of-Why (GROW) seminar, a causal reading group at Stanford University (with Guillaume Basse and Dominik Rothenhäusler).
\item Co-organizer of the Banff workshop "The Interface Between Selective Inference and Machine Learning" (with Will Fithian, Rina Barber and Daniel Yekutieli, cancelled due to the pandemic).
\item Co-organizer of the Banff workshop "Causal Inference with Big Data" (with Peng Ding, Marloes Maathuis and Fabrizia Mealli, cancelled due to the pandemic).
\end{itemize}
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
