\documentclass{article}
\usepackage[left = 3cm, right = 3cm]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

\makeatletter
\renewcommand*{\UrlTildeSpecial}{%
  \do\~{%
    \mbox{%
      \fontfamily{ptm}\selectfont
      \textasciitilde
    }%
  }%  
}%    
\let\Url@force@Tilde\UrlTildeSpecial
\makeatother

\begin{document}
\begin{Huge}
\noindent Lihua Lei
\end{Huge}

\vspace{5mm}
\begin{minipage}{0.5\linewidth}
  \flushleft
\noindent 397 Evans Hall, University Dr. \\
\noindent Berkeley, CA 94720
\end{minipage}
\hfill
\begin{minipage}{0.5\linewidth}
  Website: \url{https://www.stat.berkeley.edu/~lihua.lei/}\\
  Email: \,\,\,\,\,lihua.lei@berkeley.edu
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Education}
\end{large}
\vspace{5mm}

\begin{minipage}{0.65\linewidth}
\noindent Ph.D. Statistics, University of California, Berkeley.\\
Advisors: Peter, J. Bickel, and Michael, I. Jordan.\\

\noindent B.S. Statistics, Peking University. \\
Undergraduate Thesis Advisor: Song Xi, Chen.
\end{minipage}\hfill
\begin{minipage}{0.34\linewidth}
\flushright
8/2014 - 8/2019 (Expected)  \\
~\\
~\\
9/2010 - 6/2014\\
\end{minipage}

\vspace{5mm}
\begin{large}
\noindent \textbf{Awards}
\end{large}
\vspace{5mm}

Citadel Fellowship, 2017-2018.

\vspace{2mm}

Outstanding Graduate Stundent Instructor Award, 2016.

\vspace{2mm}
ICML (International Conference on Machine Learning) Travel Award, 2016.

\vspace{2mm}
ACIC (Atlantic Causal Inference Conference) Travel Award, 2018.

\vspace{2mm}
Scholarship from The Sally and Terry Speed Graduate Support Fund, 2015.

\vspace{5mm}
\begin{large}
\noindent \textbf{Teaching Experiences}
\end{large}
\vspace{5mm}

TA, Statistics 210A, Theoretical Statistics A, Fall 2015 (taught by Michael, I. Jordan). 

% \vspace{2mm}
% Lecturer, Complementary Session for Statistics 210A, Fall 2015.

% \hspace{4mm} Self-prepared weekly lectures, covering Bayesian inference and hypothesis testing.

\vspace{2mm}
TA, Statistics 210B, Theoretical Statistics B, Spring 2016 (taught by Martin, J. Wainright). 

% \vspace{2mm}
% Lecturer, Complementary Session for Statistics 210B, Spring 2016.

% \hspace{4mm} Self-prepared weekly lectures, covering learning theories, concentration inequalities, 

% \hspace{4mm} high dimensional geometry, sparse linear regression, compressed sensing and kernel theories.

\vspace{5mm}
\begin{large}
\noindent \textbf{Research Experiences}
\end{large}
\vspace{5mm}

\begin{large}
\noindent Research Interests
\end{large}

\vspace{3mm}
High dimensional statistical inference; Multiple hypothesis testing; Network analysis; 

Causal Inference; Resampling methods; Stochastic optimization

\vspace{3mm}

\begin{large}
\noindent Journal Publications
\end{large}

\begin{enumerate}
\item \textbf{Lei, L.}, \& Fithian, W. (2018). AdaPT: An Interactive Procedure For Multiple Testing With Side Information. To appear in \emph{Journal of the Royal Statistical Society: Series B (JRSS-B).}
\item \textbf{Lei, L.}, Bickel, P. J., \& El Karoui, N. (2018). Asymptotics For High Dimensional Regression M-Estimates: Fixed Design Results. To appear in \emph{Probability Theory and Related Fields (PTRF)}.
\item Chen, S. X., \textbf{Lei, L.}, \& Tu, Y. (2016). Functional Coefficient Moving Average Model with Applications to forecasting Chinese CPI. \emph{Statistica Sinica}, 26, 1649-1672.
\end{enumerate}

\begin{large}
\noindent Conference Publications
\end{large}

\begin{enumerate}
\item Ye, Y., \textbf{Lei, L.}, \& Ju, C. (2018). HONES: A Fast and Tuning-free Homotopy Method For Online Newton Step. To appear in \emph{Proceedings of the 20th International Conference on Artificial Intelligence and Statistics (AISTATS)}.
\item \textbf{Lei, L.}, Ju, C., Chen, J., \& Jordan, M. I. (2017). Nonconvex Finite-Sum Optimization Via SCSG Methods. In \emph{Proceedings of the 30th Advances in Neural Information Processing Systems (NIPS)}.
\item \textbf{Lei, L.}, \& Jordan, M. I. (2017). Less than a Single Pass: Stochastically Controlled Stochastic Gradient. In \emph{Proceedings of the 20th International Conference on Artificial Intelligence and Statistics (AISTATS)}.
\item \textbf{Lei, L.}, \& Fithian, W. (2016). Power of Ordered Hypothesis Testing. In \emph{Proceedings of the 33th International
Conference on Machine Learning}.
\end{enumerate}

\begin{large}
\noindent Preprints and Submissions
\end{large}

\begin{enumerate}
\item D'Amour, A., Ding, P., Feller, A., \textbf{Lei, L.}, \& Sekhon, J. (2017) Overlap in High Dimensional Observational Studies. \emph{ArXiv e-prints, abs/1711.02582.}
\item \textbf{Lei, L.}, Ramdas, A., \& Fithian, W. (2017) STAR: A General Interactive Framework For FDR Control Under Structural Constraints. \emph{ArXiv e-prints, abs/1710.02776}.
\item \textbf{Lei, L.} \& Ding, P. (2018) Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{ArXiv e-prints, abs/1806.07585}.
\item Li, T., \textbf{Lei, L.}, Bhattacharyya, S., Sarkar, P., Bickel, P. J., \& Levina, E. (2019) Hierarchical community detection by recursive partitioning. \emph{ArXiv e-prints, abs/1810.01509}.
\item \textbf{Lei, L.} \& Jordan, M. I. (2019) On the Adaptivity of Stochastic Gradient-Based Optimization. \emph{ArXiv e-prints, abs/1904.04480}.
\end{enumerate}

% \begin{large}
% \noindent Ongoing works (to be posted on arxiv soon)
% \end{large}

% \begin{enumerate}
% \item \textbf{Lei, L.} \& Bickel, P. J.. Tighter $\ell_{\infty}$ Perturbation Theory for Eigenvectors of Binary Wigner Matrices.
% \item \textbf{Lei, L.} \& Bickel, P. J.. CPT: An Assumption-Free Exact Test For Linear Models With Exchangeable Errors.
% \item \textbf{Lei, L.} \& Jordan, M. I.. Adaptivity of Stochastic Gradient-Based Optimization.
% \item Ye, Y., \textbf{Lei, L.} \& Jordan, M. I.. Bayesian Inference On Gaussian Graphical Models With Soft G-Wishart Distributions.
% \item Yang, C., \textbf{Lei, L.}, Ho, N., \& Fithian, W.. BONuS: Interactively determining an optimal test statistic in multiple multivariate testing.
% \item \textbf{Lei, L.} \& Jordan, M. I.. High Dimensional Edgeworth Expansion and Applications to Bootstrap and Its Variations.
% \item \textbf{Lei, L.} \& Jordan, M. I.. G-SGD: Adaptive Stochastic Gradient Method Via Geometrization.
% \item \textbf{Lei, L.} D'Amour, A., Ding, P., Feller, A., \& Sekhon, J.. Assumption-Free Test of Overlap In Observational Studies.
% \item \textbf{Lei, L.} \& Ding, P.. Non-asymptotic Finite Population Central Limit Theorems in Causal Inference.
% \end{enumerate}

\begin{large}
\noindent Softwares 
\end{large}

\begin{enumerate}
\item \texttt{adaptMT}: \texttt{R} package on Adaptive P-value Thresholding (on CRAN); 
\item \texttt{mkn}: \texttt{R} package on multiple knockoffs based inference (on github).
\end{enumerate}

\vspace{2mm}
\begin{large}
\noindent \textbf{Professional Services}
\end{large}
\vspace{5mm}

\begin{large}
\noindent Invited Talks
\end{large}

\vspace{2mm}
Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{Joint Statistical Meeting, Topic Contributed Session}, Aug. 2019.

\vspace{2mm}
BONuS: Interactively determining an optimal test statistic in multiple multivariate testing. \emph{ICSA China Conference}, Jul. 2019.

\vspace{2mm}
Hierarchical community detection by recursive partitioning. \emph{ICSA Applied Statistics Symposium}, Jun. 2019.

\vspace{2mm}
Model-Free Assessment of Overlap in Observational Studies. \emph{At Yale University (Department Seminar)}, Feb. 2019.

\vspace{2mm}
Hierarchical community detection by recursive partitioning. \emph{At University of California, Davis (Student Seminar)}, Jan. 2019.

\vspace{2mm}
Model-Free Assessment of Overlap in Observational Studies. \emph{At Stanford University (Stefan Wager's group)}, Jan. 2019.

\vspace{2mm}
Statistical Inference in Moderate Dimensions. \emph{At University of South California (Department Seminar)}, Dec. 2018.

\vspace{2mm}
Hierarchical community detection by recursive bi-partitioning. \emph{At University of Michigan (Liza Levina's group)}, Oct. 2018.

\vspace{2mm}
Statistical Inference in Moderate Dimensions. \emph{At University of Michigan (Student Seminar)}, Oct. 2018.

\vspace{2mm}
Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{At University of Michigan (Xuming He's group)}, Oct. 2018.

\vspace{2mm}
AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{International Conference on Econometrics and Statistics (EcoSta)}, Jun. 2018.

\vspace{2mm}
Regression Adjustment in Randomized Experiments With A Diverging Number of Covariates. \emph{Atlantic Causal Inference Conference (ACIC)}, May. 2018.

\vspace{2mm}
Stochastically Controlled Stochastic Gradient (SCSG) Method. \emph{At University of California, Davis (Cho-Jui Hsieh's group)}, Mar. 2018.

\vspace{2mm}
AdaPT: An Interactive Procedure For Multiple Testing With Side Information. \emph{At Stanford University (David Tse's group)}, Feb. 2018.

\vspace{2mm}
Asymptotics For High Dimensional Regression M-Estimates: Fixed Design Results. \emph{Berkeley-Stanford Econometrics Jamboree}, Nov. 2017. 

\vspace{5mm}

\begin{large}
\noindent Contributed Talks and Poster Presentation
\end{large}

\vspace{2mm}
Workshop on Higher-Order Asymptotics and Post-Selection Inference (WHOA-PSI), 2018.

\vspace{2mm}
European Causal Inference Meeting (EuroCIM), 2018.

\vspace{2mm}
Neural Information Processing Systems (NIPS), 2017.

\vspace{2mm}
International Conference on Multiple Comparison Procedures (MCP), 2017.

\vspace{2mm}
International Conference on Artificial Intelligence and Statistics (AISTATS), 2017.

\vspace{2mm}
Joint Statistical Meetings (JSM), 2016, 2018.

\vspace{2mm}
International Conference on Machine Learning (ICML), 2016.

\vspace{2mm}
Stanford-Berkeley Joint Colloquium, 2015, 2016, 2017.

\vspace{2mm}
Berkeley Statistics Annual Research Symposium (BSTARS), 2017, 2018.

\vspace{5mm}
\begin{large}
\noindent Reviewing
\end{large}

\vspace{2mm}
\noindent \textbf{Journals: }Annals of Statistics (AoS), Journal of the American Statistical Association (JASA), Journal of the Royal Statistical Society-Series A/B (JRSS-A, JRSS-B), Electronic Journal of Statistics (EJS), Biometrics, Journal of Causal Inference (JCL), Transactions on Pattern Analysis and Machine Intelligence (TPAMI).

\vspace{2mm}
\noindent \textbf{Conferences:} ICML, NeurlPS, AISTATS.

% \vspace{5mm}
% \begin{large}
% \noindent \textbf{Courses}
% \end{large}

% \begin{enumerate}
% \item Fall, 2014: STAT205A (Probability Theory): A+; STAT210A (Theoretical Statistics): A+; 

% \hspace{1.62cm} STAT215A (Applied Statistics): A+.
% \item Spring, 2015: STAT205B (Probability Theory): A+; STAT210B (Theoretical Statistics): A+; 

% \hspace{2.05cm} EE227C (Convex Optimization): A.
% \item Fall, 2015: EE229A (Information Theory and Coding): A+; 

% \hspace{1.62cm} STAT212A (Multiple Testing and Selective Inference): A+.
% \item Spring, 2016: EE229B (Error Control Coding): A.

% \item Fall, 2016: STAT241A (Statistical Learning): A; 

% \hspace{1.62cm} STAT240 (Nonparametric and Robust Methods): A+.
% \end{enumerate}

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
